---
title: "Credit Card Fraud Detection"
author: "Thomas Brown"
date: "24 February 2018"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Credit Card Fraud Detection

This analysis uses the credit card fraud detection dataset available on [kaggle](https://www.kaggle.com/mlg-ulb/creditcardfraud).

The goal is to construct a machine learning model that has a reasonable predictive abilitity in determining whether a credit card transaction is genuine or fraudulant.
```{r pressure, echo=FALSE, message=FALSE}


```


We will start by loading the packages that will be used for this analysis, setting up a seed for reproducability and reading in the data.
```{r prep, message=FALSE, warning=FALSE}

library(tidyverse)
library(caret)
library(PRROC)

set.seed(8549)

source <- read.csv("D:/Data/creditcard.csv")

```


Let's preview the first couple of observations from the dataset.
```{r head, echo=FALSE, message=FALSE}

head(source)


```



